---
title: <span style="font-size:24px;color:#20435b"><b>CDM Vocabulary Diff Report</b></span>
output:
  html_document:
    toc: yes
    toc_depth: 5
    toc_float:
      collapsed: false
  html_notebook: default
params:
  JSONFile: ""
---


```{r, echo=FALSE, warning=FALSE, message=FALSE}
library(DT)
library(jsonlite)

myObject = jsonlite::fromJSON(params$JSONFile)
```



**The following report compares vocabulary versions `r myObject$GetVocabVersion$PRIOR_VOCAB` 
and `r myObject$GetVocabVersion$CURRENT_VOCAB`<br>
Report generated on: `r format(Sys.time(), '%d %B, %Y')`**



<br>
<br>

#### <b><font color="#20435b">BASIC SUMMARY</font></b>

For each table in the vocabulary, display the old count, new count, and diff.<br>
This report will enable you to determine if a table has grown/shrunk and by how much.
<br>
<br>

                   
```{r, echo=FALSE, warning=FALSE, message=FALSE}

DT::datatable(as.data.frame(myObject$CountSummaryDiff), colnames = c("Table","Old Count","New Count","Diff"),
                 filter = 'top', options = list(pageLength = 10, autoWidth = TRUE))

```
<br>

#### <b><font color="#20435b">CONCEPT</font></b>

The following reports show different ways in which the data in the CONCEPT table has changed from one vocab to the next.
The reports in this section do not involve any tables other than CONCEPT.

<br>

##### <b>Domain Changes</b>

<table>
<tr>
<td style="width:150px;text-align:right;font-size:18px;vertical-align:top;padding-left:10px;padding-right:10px;">
`r format(as.data.frame(myObject$CountConceptDomainChanges),format="d",big.mark=",",scientific=FALSE)`</td>
<td style="text-align:left;vertical-align:top;padding-left:10px;padding-right:10px;font-size:12px;">
This number represents the number of concepts that experienced domain changes from one vocab to the next.<br>
This report is related to the following bug: 
<a href="https://github.com/OHDSI/Vocabulary-v5.0/issues/130">Changing Domain Bug</a>
</td>
</tr>
</table>

<br>
<br>

##### <b>Name Changes</b>

<table>
<tr>
<td style="width:150px;text-align:right;font-size:18px;vertical-align:top;padding-left:10px;padding-right:10px;">
`r format(as.data.frame(myObject$CountConceptNameChanges),format="d",big.mark=",",scientific=FALSE)`</td>
<td style="text-align:left;vertical-align:top;padding-left:10px;padding-right:10px;font-size:12px;">
This number represents the number of concepts that experienced name changes from one vocab to the next.
</td>
</tr>
</table>

<br>
<br>

##### <b>Class Changes</b>

<table>
<tr>
<td style="width:150px;text-align:right;font-size:18px;vertical-align:top;padding-left:10px;padding-right:10px;">
`r format(as.data.frame(myObject$CountConceptClassChanges),format="d",big.mark=",",scientific=FALSE)`</td>
<td style="text-align:left;vertical-align:top;padding-left:10px;padding-right:10px;font-size:12px;">
This number represents the number of concepts that experienced class changes from one vocab to the next.
</td>
</tr>
</table>

<br>
<br>

##### <b>Invalid Changes</b>

<table>
<tr>
<td style="width:150px;text-align:right;font-size:18px;vertical-align:top;padding-left:10px;padding-right:10px;">
`r format(as.data.frame(myObject$CountConceptInvalidChanges),format="d",big.mark=",",scientific=FALSE)`</td>
<td style="text-align:left;vertical-align:top;padding-left:10px;padding-right:10px;font-size:12px;">
This number represents the number of concepts that have become invalid in the new vocab.
</td>
</tr>
</table>

<br>
<br>


##### <b>Changes by vocabulary_id & domain_id</b>

This reports displays the change in distribution of rows, stratified by vocabulary_id and domain_id.<br> 
A diff > 0 represents the number of rows added in the new vocab (for a particular vocab/domain combination),<br> 
while a diff < 0 represents the number of rows lost for that combination. 
<br> 
<br>
            
```{r, echo=FALSE, warning=FALSE, message=FALSE}

DT::datatable(as.data.frame(myObject$CountConceptDiffsByDandV),filter = 'top', 
              colnames=c("Vocabulary","Domain","Old Count","New Count","Diff"),
                options = list(pageLength = 10, autoWidth = TRUE))

```

<br>
<br>

##### <b>Changes by concept_class_id</b>

This reports displays the change in distribution of rows, stratified by concept_class_id.
<br> 
<br> 

            
```{r, echo=FALSE, warning=FALSE, message=FALSE}

  DT::datatable(as.data.frame(myObject$CountConceptDiffsByClass),filter = 'top', 
                colnames=c("Class","Old Count","New Count","Diff"),
                    options = list(pageLength = 10, autoWidth = TRUE))

```

<br>
<br>

##### <b>Changes by domain_id</b>

This reports displays the change in distribution of rows, stratified by domain_id.
<br> 
<br> 

            
```{r, echo=FALSE, warning=FALSE, message=FALSE}

  DT::datatable(as.data.frame(myObject$CountConceptDiffsByDomain),filter = 'top', colnames=c("Domain","Old Count","New Count","Diff"),
                    options = list(pageLength = 10, autoWidth = TRUE))

```

<br>
<br>

##### <b>Changes by invalid_reason</b>

This reports displays the change in distribution of rows, stratified by invalid_reason.
<br> 
<br> 

            
```{r, echo=FALSE, warning=FALSE, message=FALSE}

  DT::datatable(as.data.frame(myObject$CountConceptDiffsByInvRsn),filter = 'top', 
                colnames=c("Invalid Reason","Old Count","New Count","Diff"),
                    options = list(dom='',pageLength = 10, autoWidth = TRUE))

```

<br>
<br>

##### <b>Changes by standard_concept</b>

This reports displays the change in distribution of rows, stratified by standard_concept.
<br> 
<br> 

            
```{r, echo=FALSE, warning=FALSE, message=FALSE}

  DT::datatable(as.data.frame(myObject$CountConceptDiffsByStdConcept),filter = 'top', 
                colnames=c("Standard Concept","Old Count","New Count","Diff"),
            options = list(dom='', pageLength = 10, autoWidth = TRUE))

```

<br>
<br>

##### <b>Changes by vocabulary_id</b>

This reports displays the change in distribution of rows, stratified by vocabulary_id.
<br> 
<br> 
     
            
```{r, echo=FALSE, warning=FALSE, message=FALSE}

  DT::datatable(as.data.frame(myObject$CountConceptDiffsByVocab),filter = 'top', 
                colnames=c("Vocabulary","Old Count","New Count","Diff"),
                    options = list(pageLength = 10, autoWidth = TRUE))

```

<br>
<br>

#### <b><font color="#20435b">CONCEPT_SYNONYM</font></b>
The following reports show different ways in which the data in the CONCEPT_SYNONYM table has changed from one vocab to the next. 
<br>
<br>

##### <b>Synonym Changes</b>

<br>

<table>
<tr>
<td style="width:150px;text-align:right;font-size:18px;vertical-align:top;padding-left:10px;padding-right:10px;">
`r format(as.data.frame(myObject$CountSynNameDiffs),format="d",big.mark=",",scientific=FALSE)`</td>
<td style="text-align:left;vertical-align:top;padding-left:10px;padding-right:10px;font-size:12px;">
This number represents the number of concepts that experienced synonym changes from one vocab to the next.
</td>
</tr>
</table>

<br>
<br>


#### <b><font color="#20435b">CONCEPT_ANCESTOR</font></b>

The following reports show different ways in which the data in the CONCEPT_ANCESTOR table has changed from one vocab to the next.<br>

<br>

##### <b>Orphaned Drugs</b>
This report displays the number of drugs that do not map to their ingredient.<br>
This report is related to the following bug: 
<a href="https://github.com/OHDSI/Vocabulary-v5.0/issues/136">Unmapped Ingredient Bug</a>

<br>

```{r, echo=FALSE, warning=FALSE, message=FALSE}

#  DT::datatable(as.data.frame(myObject$CountOrphanedDrugs),filter = 'top', 
#                colnames=c("Old Count","New Count","Diff"),
#                    options = list(dom='t', pageLength = 10, autoWidth = TRUE))


knitr::kable(as.data.frame(myObject$CountOrphanedDrugs),col.names=c("Old Count","New Count","Diff"))

```

<br>



##### <b>Missing Hierarchy</b>

<table>
<tr>
<td style="width:150px;text-align:right;font-size:18px;vertical-align:top;padding-left:10px;padding-right:10px;">
`r format(as.data.frame(myObject$CountLostCA),format="d",big.mark=",",scientific=FALSE)`</td>
<td style="text-align:left;vertical-align:top;padding-left:10px;padding-right:10px;font-size:12px;">
This number represents the number of ancestor/descendant row combinations that are no longer present in the current vocab.
This report is related to the following bug: 
<a href="https://github.com/OHDSI/Vocabulary-v5.0/issues/136">Unmapped Ingredient Bug</a>
</td>
</tr>
</table>
<br>

<br> 

#### <b><font color="#20435b">CONCEPT_RELATIONSHIP</font></b>

The following reports show different ways in which the data in the CONCEPT_RELATIONSHIP table has changed from one vocab to the next.

<br>
<br>


##### <b>Missing Relationships</b>


<table>
<tr>
<td style="width:150px;text-align:right;font-size:18px;vertical-align:top;padding-left:10px;padding-right:10px;">
`r format(as.data.frame(myObject$CountMissingCR),format="d",big.mark=",",scientific=FALSE)`</td>
<td style="text-align:left;vertical-align:top;padding-left:10px;padding-right:10px;font-size:12px;">
This number represents the number of missing relationships.<br>
For this report, a missing relationship is simply a concept_id_1/concept_id_2 combination 
that is no longer present in the new vocab.
</td>
</tr>
</table>
<br>
<br>

##### <b>Valid/Invalid Relationships</b>

This report displays the number of valid CR rows that map invalid standard concepts<br> 
(i.e., cr.invalid_reason is null,but at least one of the concepts is invalid when joined back to concept).

<br>

```{r, echo=FALSE, warning=FALSE, message=FALSE}

#  DT::datatable(as.data.frame(myObject$CountValidInvalidCR),filter = 'top', 
#                colnames=c("Old Count","New Count","Diff"),
#                    options = list(dom='t',pageLength = 10, autoWidth = TRUE))

knitr::kable(as.data.frame(myObject$CountValidInvalidCR),col.names=c("Old Count","New Count","Diff"))

```

<br>
<br>


##### <b>Missing Descendants 1</b>

<table>
<tr>
<td style="width:150px;text-align:right;font-size:18px;vertical-align:top;padding-left:10px;padding-right:10px;">
`r format(as.data.frame(myObject$CountMissingDescendants),format="d",big.mark=",",scientific=FALSE)`</td>
<td style="text-align:left;vertical-align:top;padding-left:10px;padding-right:10px;font-size:12px;">
This number represents the number of descendent_concept_id rows that were in the previous vocab, but not the current.
</td>
</tr>
</table>
<br>
<br>


##### <b>Missing Descendants 2</b>

Distribution of missing descendants stratified by domain, vocab, and concept class.<br>
Missing descendants are descendent_concept_id rows that were in the previous vocab, but not the current.
<br>
<br>


```{r, echo=FALSE, warning=FALSE, message=FALSE}
 DT::datatable(as.data.frame(myObject$CountMissingDescendantsByDomVocabClass),
    colnames = c("Vocabulary","Vocab Count","Domain","Domain Count","Concept","Concept Count"),
     filter = 'top', options = list(pageLength = 10, autoWidth = TRUE))

```

<br>
<br>


#### <b><font color="#20435b">CONCEPT_CLASS</font><b><br>

<table>
<tr>
<td style="width:150px;text-align:right;font-size:18px;vertical-align:top;padding-left:10px;padding-right:10px;">
`r format(as.data.frame(myObject$CountCCNDiffs),format="d",big.mark=",",scientific=FALSE)`</td>
<td style="text-align:left;vertical-align:top;padding-left:10px;padding-right:10px;font-size:12px;">
This number represents the number of changes to concept_class_name.
</td>
</tr>
</table>
<br>
<br>



#### <b><font color="#20435b">DOMAIN</font><b>

<table>
<tr>
<td style="width:150px;text-align:right;font-size:18px;vertical-align:top;padding-left:10px;padding-right:10px;">
`r format(as.data.frame(myObject$CountDomainNameDiffs),format="d",big.mark=",",scientific=FALSE)`</td>
<td style="text-align:left;vertical-align:top;padding-left:10px;padding-right:10px;font-size:12px;">
This number represents the number of domain name changes in the current vocab.
</td>
</tr>
</table>
<br>
<br>



#### <b><font color="#20435b">RELATIONSHIP</font><b><br>
This report displays the changes to the relationship table.

```{r, echo=FALSE, warning=FALSE, message=FALSE}

knitr::kable(as.data.frame(myObject$CountRelDiffs),
             row.names("Count"),col.names=c("Hierarchy","Ancestry","Rev.Rel","Rel.Concept"))
```

<br>
<br>

